Cyclone: Fault Tolerance Middleware for NVM Clusters

### 2016-06-18 paper/paper.tex
Updates to paper.

>>>>

\section{Concurrency}
\subsection{Network}
The single leader in RAFT must send a message to every replica and receive a
response from every replica to replicate a log entry. The number of
messages the leader must handle grows therefore with the number of replicas
while follower replicas only handle a fixed number of
messages for each log entry. This imbalance causes the leader to become a
bottleneck at high throughputs for even a small number of replicas.

In order to ease this bottleneck, Cyclone allows clients to assist in
replication. To do so with minimum changes to the RAFT protocol, the leader
continues to replicate entries to clients on a timeout, with the clients
providing best effort replication. The flow for assisted replication is
simple. For any RPC call added to the log, the leader sends back a message to
the client with a list of replicas. The client then sends the RPC call to
follower replicas on behalf of the leader. It then then waits for a timeout,
gathers and sends back a message to the leader with the list of replicas that
have responded within the timeout. Client assisted replication is therefore best
effort. The leader also continues to run the normal RAFT protocol - in the event
that a log entry remains unreplicated at a follower it sends it the log entry
for replication as usual.

The only change necessary for client assisted replication from the perspective
of RAFT is for follower replicas to be able to handle out of order arrival of
log entries. This is accomplished by an in memory cache of replicated log
entries. When an arriving entry completes a sequence of log entries starting at
the next desired index, the cache attempts to append the log entries to the
actual RAFT log. For each entry the appropriate RAFT response (accept/reject) is
sent back to the client that had sent the entry on behalf of the leader.
